\section{Functional requirements}
The description of the requirements of a general voting application can be found in the security requirement section. In this section we will discuss these requirement and how they fit into a electronic voting application.





\begin{description}
    \item [Voter Privacy]
        No one should be able to link a vote back to the specific voter, and only the voter should
        know his vote. These requirements shall hold during and after the election.  
    
    \item [Eligibility]    
        Only Eligible and registered voters can vote. 
    
    \item [Uniqueness]
        Only one vote per registered voter should be counted.
    
    \item [Fairness]
        None should be able to gain any knowledge of the outcome of the election, before the ending. This is to prevent voters of voting accordingly to any leaked information. 
    
    \item [Uncoercibility]
        Nobody should be able to extract the value of a vote. This is to prevent anybody from compelling a voter by force, intimidation, or authority to cast a vote in a specific way. 
    
    \item [Receipt-freeness] 
        The voting system should not produce a receipt that reveals any information about the casted vote. This is to prevent a vote from trading his vote. 
    
    \item [Accuracy] 
        The final tally should be correctly computed from valid casted votes. It should not be
        possible to manipulate the final tally without being detected. 
    
    \item [Universal Verifiabilit]
        It should be possible for any participants and observers to validate individual votes as well as the final tally of the election. 
    
    \item [Individual Verifiability]    
        Every registered voter should be able to verify that his vote is counted correctly. 
    
\end{description}
